The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes behind AO-fed coronagraphs

### 2021-03-13 specklelives.tex
update

\clearpage
\section{Discussion}
For some time, long-lived quasi-static speckles have been recognized as the limiting noise source in contemporary high contrast imaging observations \citep[e.g.][]{2007ApJ...654..633H}.  Given their origin within the instrument, and comparatively long lifetimes \citep{2012A&A...541A.136M}, such speckles should be supressable using wavefront sensing and control strategies.  Recent progress in applying ``dark hole'' contrast optimization with focal plane WFS \citep{2020A&A...638A.117P} and various low-order coronagraphic WFS\&C strategites \citep[e.g.][]{2017PASP..129i5002S} show great promise in significantly reducing the impact of internal speckles.  Assuming active quasi-static speckle control becomes routine, the fundamental limit to sensitivity in ground-based high-contrast imaging is set by the Earth's atmosphere.  This limit is set by two components: uncorrelated photon noise and the spatially and temporally correlated speckle noise.  The temporal correlations of atmospheric speckles are, compared to quasi-static speckles, relatively short. This precludes conventional post-processing, but the lifetimes are long enough to significantly increase exposure times compared to the photon-noise.

>>>>

\clearpage
\section{Discussion}
For some time, long-lived quasi-static speckles have been recognized as the limiting noise source in contemporary high contrast imaging observations \citep[e.g.][]{2007ApJ...654..633H}.  Given their origin within the instrument, and comparatively long lifetimes \citep{2012A&A...541A.136M}, such speckles should be supressable using wavefront sensing and control strategies.  Recent progress in applying ``dark hole'' contrast optimization with focal plane WFS \citep{2020A&A...638A.117P} and various low-order coronagraphic WFS\&C strategites \citep[e.g.][]{2017PASP..129i5002S} show great promise in significantly reducing the impact of internal speckles.  Assuming active quasi-static speckle control becomes routine, the fundamental sensitivity limit in ground-based high-contrast imaging is set by the Earth's atmosphere.  This limit is set by two components: uncorrelated photon noise and the spatially and temporally correlated speckle noise.  The temporal correlations of atmospheric speckles are, compared to quasi-static speckles, relatively short. This precludes conventional post-processing, but the lifetimes are long enough to significantly increase exposure times compared to the photon-noise.
